Laplacian envelope

### 2015-06-02 Notes/laplace.tex
optimisers with fp~=0.5
perturbations

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{ideal}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CI}{\mathcal{I}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Laplacian envelope}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

This results in
%
\begin{equation}\label{eq:overlapwt}
\begin{aligned}
  \av{\syn^1_\text{ideal}\syn^1(t)} &= \eq (f\pot\M\pot-f\dep\M\dep)\, \e^{(r\frg+\hom)t} \w, \\
  \av{\syn^1_\text{ideal}\syn^1(\infty)} &= \eq (f\pot\M\pot-f\dep\M\dep)\, \onev\eq \w \\
         &= \eq (f\pot\onev-f\dep\onev)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \e^{(r\frg+\hom)t} \w .
\end{aligned}
\end{equation}
%
Combining these allows us to write the numerator of \eqref{eq:SNRdef} as
%
\begin{equation}\label{eq:signal}
\begin{aligned}
  \av{\syn_\text{ideal}\cdt\syn(t)} - \av{\syn_\text{ideal}\cdt\syn(\infty)}
    &= N \eq \enc \, \e^{(r\frg+\hom)t} \w , \\
    \text{where} \qquad
  \enc &= f\pot(\M\pot-\I)-f\dep(\M\dep-\I)
\end{aligned}
\end{equation}
%
Combining with \eqref{eq:noise} gives
%
\begin{equation}\label{eq:SNRcurveExact}
  \SNR(t) = \frac{\sqrt{N} \eq \enc\,\e^{(r\frg+\hom)t}\w}
                 {\sqrt{1-(f\pot-f\dep)^2(\eq_+-\eq_-)^2}}.
\end{equation}
%
We can absorb $\hom$ into $\MM\potdep$ by defining
%
\begin{equation}\label{eq:absorbhom}
\begin{aligned}
  \Mh\potdep &= \M\potdep + \frac{\hom}{2rf\potdep},
  &\qquad
  \frgh &= f\pot\Mh\pot + f\dep\Mh\dep - \I,
  \\&&
  \ench &= f\pot(\Mh\pot-\I)-f\dep(\Mh\dep-\I).
\end{aligned}
\end{equation}
%
Then the SNR curve is
%
\begin{equation}\label{eq:SNRcurvehom}
  \SNR(t) = \frac{\sqrt{N}  \eq \ench \,\e^{rt\frgh}\w}
                 {\sqrt{1-(f\pot-f\dep)^2(\eq_+-\eq_-)^2}}.
\end{equation}
%
The denominator will not play any role in what follows, as the models that maximize the various measures of memory performance all have some sort of balance between potentiation and depression, either with $f\pot=f\dep$ or $\eq_+=\eq_-$.
We can perform the maximisation in two steps.
First maximise the numerator at fixed $\eq\w$.
Then maximise the ratio \wrt $\eq\w$.
This will allow us to ignore the denominator until the very end.

@@

We can then treat the off-diagonal elements of $\Mh\potdep$ as the independent degrees of freedom, subject to these constraints, when maximising the SNR.
The diagonal elements are determined by setting the row sums to 1.
We then have
%
\begin{equation}\label{eq:derivpd}
  \pdiff{\Mh\pot_{ij}}{\Mh\pot_{mn}{}} = \pdiff{\Mh\dep_{ij}}{\Mh\dep_{mn}{}} = \delta_{im}(\delta_{jn}-\delta_{jm}),
  \qquad
  \pdiff{\Mh\pot_{ij}}{\Mh\dep_{mn}{}} = \pdiff{\Mh\dep_{ij}}{\Mh\pot_{mn}{}} = 0.
\end{equation}
%
It will also be convenient to define the differential operators
%
\begin{equation}\label{eq:pertfe}
  \pdiff{}{\frgh_{ij}{}} = \frac{1}{2f\pot} \pdiff{}{\Mh\pot_{ij}{}} + \frac{1}{2f\dep} \pdiff{}{\Mh\dep_{ij}{}},
  \qquad
  \pdiff{}{\ench_{ij}{}} = \frac{1}{2f\pot} \pdiff{}{\Mh\pot_{ij}{}} - \frac{1}{2f\dep} \pdiff{}{\Mh\dep_{ij}{}},
\end{equation}
%
these satisfy
%
\begin{equation}\label{eq:derivfe}
  \pdiff{\frgh_{ij}}{\frgh_{mn}{}} = \pdiff{\ench_{ij}}{\ench_{mn}{}} = \delta_{im}(\delta_{jn}-\delta_{jm}),
  \qquad
  \pdiff{\frgh_{ij}}{\ench_{mn}{}} = \pdiff{\ench_{ij}}{\frgh_{mn}{}} = 0.
\end{equation}
%

@@

In analogy to the generalised fundamental matrix of a Markov chain \cite{Kemeny1981fund}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s\I +\onev\pib -\MM)\inv,
\end{equation}
%
where $\pib$ is an arbitrary row vector satisfying $\pib\onev = \frac{1}{\tau_0} \neq 0$.
This reduces to the fundamental matrix at $s=0$.
We can see that $\onev$ is an eigenvector:
%
\begin{equation}\label{eq:lfundrowsum}
  \fund(s)\onev = \frac{\tau_0}{1+s\tau_0}\onev.
\end{equation}
%
Suppose we have some row vector $\mathbf{a}$ such that $\mathbf{a}\onev=0$.
Then $\mathbf{a}\fund(s)$ is independent of $\pib$:
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\pib_k} = (\mathbf{a}\fund(s)\onev) \fund_{ki}(s) 
      = \frac{\tau_0}{1+s\tau_0} (\mathbf{a}\onev) \fund_{ki}(s) = 0.
\end{equation}
%

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurvehom} (ignoring the denominator)
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) &= \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) \\
   &= \intd[_0^{\infty}]{t} \sqrt{N} \eq \ench \e^{(r\frgh-s)t} \w \\
   &= \sqrt{N} \eq \ench \prn{s - r\frgh}\inv \w.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\ench\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = \frac{A(s)}{\sqrt{N}} &=  \eq \ench \fund(s) \w \\
    &= \sum_{ijk} \eq_i \ench_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= \sum_{ij}  \eq_i \ench_{ij} (\eta^w_{i}(s) - \eta^w_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.

@@

Using the same approach as the area bound in \cite{Lahiri2013synapse}, we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
\begin{aligned}
  \pdiff{\hat{A}(s)}{\Mh\potdep_{mn}{}}
     =&\, rf\potdep \eq_m \brk{ \sum_i (\fptb_{mi}(0)-\fptb_{ni}(0)) a_i(s)
     +c_m(s) (\eta^w_m(s) - \eta^w_n(s)) } \\
     &\pm f\potdep \eq_m (\eta^w_m(s) - \eta^w_n(s)).
\end{aligned}
\end{equation}
%

@@

%
\begin{equation}\label{eq:areadef}
  \int[_0^\infty]{dt} \snr(t) = \lim_{\tau\to\infty} \tau \snrb(\tau) = A(0).
\end{equation}
%

The only effect of $\hom$ is in the diagonal constraints (second column of \eqref{eq:constrh} vs.\ second inequality in \eqref{eq:constri}).
However, the area is invariant under the scaling mode:
%
\begin{equation}\label{eq:scale}
  \Mh\potdep - \I \to \lambda (\Mh\potdep - \I).
\end{equation}
%
This means we can always take a set of matrices that violate either version of the diagonal constraints and use \eqref{eq:scale} to create a set of matrices that satisfy them without changing the area.
Therefore, including $\hom$ has no effect on the area bound and the result from \cite{Lahiri2013synapse} applies here as well.

This means that 
%
\begin{equation}\label{eq:areabnd}
  A(0) \leq \frac{\sqrt{N}(M-1)}{r}.
\end{equation}
%
The model that saturates this bound is one of serial topology with $\eq$ concentrated symmtrically at the two end states.

@@

%
\begin{equation}\label{eq:initdef}
  \snr(0) = \snrb(0) = \lim_{s\to\infty} sA(s).
\end{equation}
%

%
\begin{equation}\label{eq:initbnd}
  \snr(0) \leq \sqrt{N},
\end{equation}
%
at least when $f\pot=f\dep=\frac{1}{2}$.

@@

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{ideal}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CI}{\mathcal{I}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}

% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Laplacian envelope}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

This results in
%
\begin{equation}\label{eq:overlapwt}
\begin{aligned}
  \av{\syn^1_\text{ideal}\syn^1(t)} &= \eq (f\pot\M\pot-f\dep\M\dep)\, \e^{(r\frg+\hom)t} \w, \\
  \av{\syn^1_\text{ideal}\syn^1(\infty)} &= \eq (f\pot\M\pot-f\dep\M\dep)\, \onev\eq \w \\
         &= \eq (f\pot\onev-f\dep\onev)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \e^{(r\frg+\hom)t} \w .
\end{aligned}
\end{equation}
%
Combining these allows us to write the numerator of \eqref{eq:SNRdef} as
%
\begin{equation}\label{eq:signal}
\begin{aligned}
  \av{\syn_\text{ideal}\cdt\syn(t)} - \av{\syn_\text{ideal}\cdt\syn(\infty)}
    &= N \eq \enc \, \e^{(r\frg+\hom)t} \w , \\
    \text{where} \qquad
  \enc &= f\pot(\M\pot-\I)-f\dep(\M\dep-\I)
\end{aligned}
\end{equation}
%
Combining with \eqref{eq:noise} gives
%
\begin{equation}\label{eq:SNRcurveExact}
  \SNR(t) = \frac{\sqrt{N} \eq \enc\,\e^{(r\frg+\hom)t}\w}
                 {\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{equation}
%
We can absorb $\hom$ into $\MM\potdep$ by defining
%
\begin{equation}\label{eq:absorbhom}
\begin{aligned}
  \Mh\potdep &= \M\potdep + \frac{\hom}{2rf\potdep},
  &\qquad
  \frgh &= f\pot\Mh\pot + f\dep\Mh\dep - \I,
  \\&&
  \ench &= f\pot(\Mh\pot-\I)-f\dep(\Mh\dep-\I).
\end{aligned}
\end{equation}
%
Then the SNR curve is
%
\begin{equation}\label{eq:SNRcurvehom}
  \SNR(t) = \frac{\sqrt{N}  \eq \ench \,\e^{rt\frgh}\w}
                 {\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{equation}
%
The denominator will not play any role in what follows, as the models that maximize the various measures of memory performance all have some sort of balance between potentiation and depression, either with $f\pot=f\dep$ or $\eq_+=\eq_-$.
We can perform the maximisation in two steps.
First maximise the numerator at fixed $\eq\w$.
Then maximise the ratio \wrt $\eq\w$.
This will allow us to ignore the denominator until the very end.

@@

We can then treat the off-diagonal elements of $\Mh\potdep$ as the independent degrees of freedom, subject to these constraints, when maximising the SNR.
The diagonal elements are determined by setting the row sums to 1.
We then have
%
\begin{equation}\label{eq:derivpd}
  \pdiff{\Mh\pot_{ij}}{\Mh\pot_{mn}} = \pdiff{\Mh\dep_{ij}}{\Mh\dep_{mn}} = \delta_{im}(\delta_{jn}-\delta_{jm}),
  \qquad
  \pdiff{\Mh\pot_{ij}}{\Mh\dep_{mn}} = \pdiff{\Mh\dep_{ij}}{\Mh\pot_{mn}} = 0.
\end{equation}
%
It will also be convenient to define the differential operators
%
\begin{equation}\label{eq:pertfe}
  \pdiff{}{\frgh_{ij}} = \frac{1}{2f\pot} \pdiff{}{\Mh\pot_{ij}} + \frac{1}{2f\dep} \pdiff{}{\Mh\dep_{ij}},
  \qquad
  \pdiff{}{\ench_{ij}} = \frac{1}{2f\pot} \pdiff{}{\Mh\pot_{ij}} - \frac{1}{2f\dep} \pdiff{}{\Mh\dep_{ij}},
\end{equation}
%
these satisfy
%
\begin{equation}\label{eq:derivfe}
  \pdiff{\frgh_{ij}}{\frgh_{mn}} = \pdiff{\ench_{ij}}{\ench_{mn}} = \delta_{im}(\delta_{jn}-\delta_{jm}),
  \qquad
  \pdiff{\frgh_{ij}}{\ench_{mn}} = \pdiff{\ench_{ij}}{\frgh_{mn}} = 0.
\end{equation}
%

If we wish to use the off-diagonal elements of $\frgh$ and $\ench$ as the degrees of freedom, the constraints are
%
\begin{equation}\label{eq:constrfe}
\begin{aligned}
  \frgh_{i \neq j}   &\geq \abs{ \ench_{i \neq j} }, &\qquad
  \sum_{j\neq i} \brk{ \ench_{ij} }_+ &\leq f\pot, \\
  \sum_j \frgh_{ij} &=0, &
  \sum_{j\neq i} \brk{ \ench_{ij} }_- &\geq -f\dep, \\
  \sum_j \ench_{ij} &=0.
\end{aligned}
\end{equation}
%

@@

In analogy to the generalised fundamental matrix of a Markov chain \cite{Kemeny1981fund}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s\I +\onev\pib -\MM)\inv,
\end{equation}
%
where $\pib$ is an arbitrary row vector satisfying $\pib\onev = \frac{1}{\tau_0} \neq 0$.
This reduces to the fundamental matrix at $s=0$.
We can see that $\onev$ is an eigenvector:
%
\begin{equation}\label{eq:lfundrowsum}
  \fund(s)\onev = \frac{\tau_0}{1+s\tau_0}\onev.
\end{equation}
%
Suppose we have some row vector $\mathbf{a}$ such that $\mathbf{a}\onev=0$.
Then $\mathbf{a}\fund(s)$ is independent of $\pib$:
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\pib_k} = -(\mathbf{a}\fund(s)\onev) \fund_{ki}(s)
      = -\frac{\tau_0}{1+s\tau_0} (\mathbf{a}\onev) \fund_{ki}(s) = 0.
\end{equation}
%

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurvehom} (ignoring the denominator)
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) &= \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) \\
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \ench \e^{(r\frgh-s)t} \w }{ \sqrt{1-(f\pot-f\dep)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \ench \prn{s - r\frgh}\inv \w }{\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\ench\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = A(s) \sqrt{\frac{{{1-(f\pot-f\dep)^2(\eq\w)^2}}}{N}}  &=  \eq \ench \fund(s) \w \\
    &= \sum_{ijk} \eq_i \ench_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= \sum_{ij}  \eq_i \ench_{ij} (\eta^w_{i}(s) - \eta^w_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.

@@

Using the same approach as the area bound in \cite{Lahiri2013synapse}, we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
  \pdiff{\hat{A}(s)}{\Mh\potdep_{mn}}
     = f\potdep \eq_m \brk{ \sum_i r[\fptb_{mi}(0)-\fptb_{ni}(0)]\, a_i(s)
     +[rc_m(s) \pm 1] [\eta^w_m(s) - \eta^w_n(s)] } 
\end{equation}
%

@@

The area under the SNR curve is:
%
\begin{equation}\label{eq:areadef}
  \intd[_0^\infty]{t} \snr(t) = \lim_{\tau\to\infty} \tau \snrb(\tau) = A(0).
\end{equation}
%

The only effect of $\hom$ is in the diagonal constraints (second column of \eqref{eq:constrh} vs.\ second inequality in \eqref{eq:constri}).
However, the area is invariant under the scaling mode:
%
\begin{equation}\label{eq:scale}
  \Mh\potdep  \to (1-\lambda)\I + \lambda \Mh\potdep .
\end{equation}
%
This means we can always take a set of matrices that violate either version of the diagonal constraints and use \eqref{eq:scale} to create a set of matrices that satisfy them without changing the area.
Therefore, including $\hom$ has no effect on the area bound and the result from \cite{Lahiri2013synapse} applies here as well.

This means that
%
\begin{equation}\label{eq:areabnd}
  A(0) \leq \frac{\sqrt{N}(M-1)}{r}.
\end{equation}
%
The model that saturates this bound is one of serial topology with $\eq$ concentrated symmetrically at the two end states.

@@

The initial SNR is:
%
\begin{equation}\label{eq:initdef}
  \snr(0) = \snrb(0) = \lim_{s\to\infty} sA(s).
\end{equation}
%

This satisfies the inequality
%
\begin{equation}\label{eq:initbnd}
  \snr(0) \leq \sqrt{N},
\end{equation}
%
at least when $f\pot=f\dep=\frac{1}{2}$.

@@

\section{Finite time}\label{sec:finite}

Now we'll maximise $\snrb(\tau)$ for some fixed $\tau$, subject to the constraints \eqref{eq:constrh}.
First, we will maximise the numerator of \eqref{eq:lsnr} holding $\eq\w$ fixed. 
We can maximise the ration \wrt $\eq\w$ later.
Consider the Lagrangian
%
\begin{equation}\label{eq:finitelagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eq_i \ench_{ij} (\eta^w_i(s) - \eta^w_j(s))
        +\sum_{i\neq j} \prn{ f\pot\mu\pot_{ij} \Mh\pot_{ij} + f\dep\mu\dep_{ij} \Mh\dep_{ij} }\\
        &+\sum_i \prn{ \mu\pot_{ii} \brk{ f\pot - \sum_{j\neq i} \theta_{ij} \ench_{ij} } }
        +\sum_i \prn{ \mu\dep_{ii} \brk{ f\dep + \sum_{j\neq i} \bar{\theta}_{ij} \ench_{ij} } } \\
        &+ \lambda \prn{ \Delta\pr - \sum_i \eq_i\w_i },
\end{aligned}
\end{equation}
%
where $\theta_{ij} = 1-\bar{\theta}_{ij} = \Theta(\ench_{ij})$ and $\Delta\pr$ is the constant value we are holding $\eq\w$ at.
After maximising
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTfinite}
  \pdiff{\CL}{\Mh\potdep_{ij}} = 0, \quad
  \mu\potdep_{ij} \geq 0, \quad
  \pdiff{\CL}{\mu\potdep_{ij}} \geq 0, \quad
  \mu\potdep_{ij}\pdiff{\CL}{\mu\potdep_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
The derivatives, for $m \neq n$ are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \frac{1}{f\potdep} \pdiff{\CL}{\Mh\potdep_{mn}} =& \,  
     \eq_m \brk{ \sum_i r[\fptb_{mi}(0)-\fptb_{ni}(0)]\, a_i(s)
     +[rc_m(s) \pm 1] [\eta^w_m(s) - \eta^w_n(s)] } \\
     &+ \mu\potdep_{mn} \mp  \theta_{mn} \mu\pot_{mm} \pm  \bar{\theta}_{mn} \mu\dep_{mm} \\
     &+ \lambda \eq_m \sum_i (\fptb_{mi}(0)-\fptb_{ni}(0)) \eq_i\w_i.
\end{aligned}
\end{equation}
%
Below, we will consider various combinations of these derivatives that preserve $\eq$.

\subsection{Increasing \texorpdfstring{$c_k$}{c(k)}}\label{sec:areacoeffincr}

Consider the following combinations of derivatives:
%
\begin{equation}\label{eq:areacoeffincrderiv}
    \Delta_{mn} \equiv
      \frac{1}{\eq_{m}} \pdiffc{}{\frgh_{mn}}
      + \frac{1}{\eq_n} \pdiffc{}{\frgh_{nm}}, 
\end{equation}
%

One can show that the equilibrium probabilities, $\eq$, are invariant under these operators:
%
\begin{equation}\label{eq:sareacoeffincrprob}
  \Delta_{mn} \eq_i = 0,
\end{equation}
%
which makes it possible to integrate the perturbation:
%
\begin{equation}\label{eq:areacoeffincrfinite}
  \Mh\potdep \to \Mh\potdep + \frac{\D\boldsymbol{\epsilon}}{2f\potdep},
  \qquad
  \begin{aligned}
  \boldsymbol{\epsilon} &= \boldsymbol{\epsilon}\trans,
  \\
  \boldsymbol{\epsilon} \onev &= 0.
  \end{aligned}
\end{equation}
%
But more interestingly:
%
\begin{align}
%  \begin{aligned}
\label{eq:areacoeffincr}
    \Delta_{mn}\CL &=
      \frac{\mu\pot_{mn} + \mu\dep_{mn}}{2\eq_m} + \frac{\mu\pot_{nm} + \mu\dep_{nm}}{2\eq_n}
      + r\prn{c_m(s)-c_n(s)}\prn{\eta^w_{m}(s) - \eta^w_{n}(s)},\\
%  \end{aligned}
\end{align}
%
where $c_k$ were defined in \eqref{eq:lareacoeffs}.
As this derivative is zero at a maximum, and the $\mu\potdep_{ij}$ are non negative, the last term must be nonpositive.
Therefore, if we arrange the states in order of decreasing $\eta^w_i(s)$, the $c_k(s)$ must be nondecreasing.

\subsubsection{Shortcuts}\label{sec:shortcuts}

Now consider the following combinations of derivatives for $n>1$:
%
\begin{align}
%  \begin{aligned}
\label{eq:shortcutderiv}
    \widetilde{\Delta}_{m,n} &\equiv
      \brk{ \sum_{k=0}^{n-1} \frac{1}{\eq_{m+k}} \pdiffc{}{\frgh_{m+k,m+k+1}} }
      - \frac{1}{\eq_m} \pdiffc{}{\frgh_{m,m+ n}}.
%  \end{aligned}
\end{align}
%

One can show that the equilibrium probabilities, $\eq$, are invariant under these operators:
%
\begin{equation}\label{eq:shortcutprob}
  \widetilde{\Delta}_{m,n} \eq_i = 0,
\end{equation}
%
which makes it possible to integrate the perturbation:
%
\begin{equation}\label{eq:shortcutfinite}
  \Mh\potdep \to \Mh\potdep + \frac{\D\boldsymbol{\epsilon}^{(m,n)}}{2f\potdep},
  \qquad
  \begin{aligned}
    &\prn{\boldsymbol{\epsilon}^{(m,n)}}_{m,m+n}
      &\!\!\!\!\!\!&= -\epsilon,\\
    &\prn{\boldsymbol{\epsilon}^{(m,n)}}_{m+k,m+k+1}
      &\!\!\!\!\!\!&= \epsilon
        &\;
        &\forall\, k \in [0,n-1],\\
    &\prn{\boldsymbol{\epsilon}^{(m,n)}}_{m+k,m+k}
      &\!\!\!\!\!\!&= -\epsilon
        &
        &\forall\, k \in [1,n-1].
  \end{aligned}
\end{equation}
%
But more interestingly for our purposes:
%
\begin{equation}\label{eq:shortcutarea}
\begin{aligned}
    \widetilde{\Delta}_{m,n}\CL =& \,
      \brk{ \sum_{k=0}^{n-1} \frac{\mu\pot_{m+k,m+k+1}+\mu\dep_{m+k,m+k+1}}{\eq_{m+k}}
      - \frac{\mu\pot_{m,m+n}+\mu\dep_{m,m+n}}{\eq_m}} \\
      &+ r \sum_{k=0}^{n-1} \prn{\eta^w_{m+k}(s) - \eta^w_{m+k+1}(s)} \prn{c_{m+k}(s) - c_{m}(s)},
\end{aligned}
\end{equation}
%

If we put the states in order of decreasing $\eta^w_k(s)$, the results of the \sref{sec:areacoeffincr} tell us that the $c_k(s)$ are non-decreasing.
This implies that the last term of the final expression in \eqref{eq:shortcutarea} is non-negative.
If it is non-zero (there would need to be a lot of degeneracy for it to be zero), this would imply that $\mu\potdep_{m,m+n}>0$, which in turn implies that $\Mh\potdep_{m,m+n}=0$ for all $n>1$. NO! ONLY ONE OF THEM.

A similar technique also works for $n<1$.
This implies that the only nonzero off-diagonal transitions are nearest neighbour.
